Constant-sized correlations are sufficient to robustly self-test maximally entangled states with unbounded dimension

### 2019-09-14 Draft/draft.tex
QIP version

% AMS
\usepackage{amsmath,amssymb,amsfonts,amsthm,amstext}

@@

\renewcommand{\Re}{\operatorname{Re}}
\renewcommand{\Im}{\operatorname{Im}}
\DeclareMathOperator{\vc}{vec}
\DeclareMathOperator{\spn}{span}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\spec}{spec}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\hook}{hook}
\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\supp}{supp}

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\EXT}{EXT}
\newcommand{\LS}{LS}
\newcommand{\COMM}{COMM}
\newcommand{\EPR}[1]{\Sigma^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\tP}{\tilde{P}}
\newcommand{\tQ}{\tilde{Q}}
\newcommand{\tM}{\tilde{M}}
\newcommand{\tN}{\tilde{N}}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}
\newcommand{\nr}{n(r)}
\newcommand{\mr}{m(r)}
\newcommand{\ux}{\underline{x}}
\newcommand{\uc}{\underline{c}}
\newcommand{\ua}{\underline{a}}
\newcommand{\ub}{\underline{b}}
\newcommand{\fC}{\mathfrak{C}}
\newcommand{\ba}{\pmb{a}}
\newcommand{\bb}{\pmb{b}}
\newcommand{\bc}{\pmb{c}}
\newcommand{\bS}{\mathrm{S}}

@@

\author[1]{Honghao Fu}
\author[1,2]{Carl Miller}

@@

\affil[1]{Department of Computer Science, Institute for Advanced Computer Studies, and Joint Center for Quantum \break Information and Computer Science, University of Maryland, College Park, MD 20742, USA}
\affil[2]{National Institute of Standards and Technology, 100 Bureau Dr., Gaithersbug, MD 20899, USA}
\maketitle

\begin{abstract}
	We show that for any prime odd integer $d$ with primitive $r$, there exists a correlation of size
	$\Theta(r^2)$ 
	that can robustly self-test a maximally entangled state of dimension $4d-4$. Our result is
	inspired by the robust self-testing result by Bamps and Pironio (\textit{Physical Review A} $91.5$ $(2015)$) and
	techniques introduced by Slofstra (\textit{Forum of Mathematics, Pi}. Vol. $7$, $2019$). Since there are
	infinitely many prime numbers with primitive root at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimension.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
Self-testing is a unique phenomenon of quantum mechanics.
It is also powerful because only classical interactions are required.
It has many applications in quantum
delegated computation \cite{ruv2013,coladan2017verifier} and device independent quantum cryptography
\cite{mayersyao,vv2014,miller2017,fu2018,eat2018}.

The case of self-testing $2$-dimensional EPR pair, which is defined by
\begin{align*}
    \ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11}),
\end{align*}
is fully understood.
The techniques for robustly self-testing $\ket{EPR}$ is 
first introduced in Ref.~\cite{mckague2012}, then improved in Ref.~\cite{bamps2015}. 
Ref.~\cite{yang2013} proved an generalized swap-isometry
that can be used to robustly self-test large dimensional maxially entangled states.
Its ideas are realized later in Ref.~\cite{coladan2017all}, 
which proved that all pure bipartite entangled state 
can be self-tested.
The authors constructed a family of correlations such
that each partially or maximally entangled state of any local dimension has
a self-testing correlation in this family.
% One can also self-test many copies of the $2$-dimensional EPR
% pair in parallel \cite{mckague2016,natarajan2017,coladan2016parallel}.
% The most efficient way uses $O(\log n)$ bits question and
% answers to self-test $n$ copies of $2$-dimensional EPR
% pair \cite{lowdegree}.
% Self-testing general $d$-dimensional EPR pairs is a harder task.
% Coladangelo, Goh and Scarani has shown that all pure bipartite entangled states can be self-tested \cite{coladan2017all}
To generate a correlation in the family, Alice and Bob
have constant number of measurement settings but each 
measurement setting has the same number of outcomes as
the local dimension of the entangled state to be self-tested. 
In other words, their correlation is of size $\Theta(d^2)$,
where $d$ is the local dimension of the entangled state.
This is the only result about self-testing the general $d$-dimensional entangled state so far.
However, proving the robustness of the family of correlations remains an open problem. 
Without robustness, we cannot infer anything about a quantum strategy if
the produced correlation deviates from the ideal correlation, no matter how small the 
deviation is.

A natural question to ask is whether maximally entangled states with large local dimension
can be robustly self-tested with constant-sized correlations. 
In this paper, we give an affirmative answer to this question by proving the following theorem.
\begin{theorem}[Informal]
\label{thm:inf}
	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
	the maximally entangled state of local dimension $4(d-1)$ can be robustly self-tested 
	with constant-sized question and answer alphabets.
\end{theorem}
The formal statement of this theorem is given in \cref{thm:self-test} and \cref{thm:infty}.

The set $D$ is, specifically, the set of all 
odd prime numbers whose smallest primitive root is either $2$, $3$, or $5$.  
It has been shown that this set has infinitely many elements \cite{murty1988}.
To prove \cref{thm:inf}, we construct a correlation of size $\Theta(r)$ 
for each $d \in D$ whose smallest primitive root is $r$.
This correlation is denoted by $\fC(d,r)$.
Note that although the size of $\fC(d,r)$ does not depend on $d$, the entries of $\fC(d,r)$ do.
Then we prove the robust self-testing property of $\fC(d,r)$ by showing 
that if some quantum strategy can approximate $\fC(d,r)$, then
the generalized swap isometry \cite{yang2013}
can produce the desired maximally entangled states when applied to the unknown state used in the strategy.
%Then the self-testing property of this correlation is 
%given in the following theorem.
%\begin{theorem}[Informal]
%\label{thm:pr_2}
%	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
%	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
%\end{theorem}
\carl{The paper \cite{bamps2015} says that the earlier paper \cite{yang2013} has ``flaws.'' Check what those flaws are, and make sure that they won't put a shadow on anything that you're discussing when you cite \cite{yang2013}.} 
\hfc{The flaws are in the self-testing proof, not in the 
proof about the generalized isometry.}

The correlation $\fC(d,r)$ contains the ideal correlation of a specially-designed binary linear system game.
In a general linear system game, Alice is given a random equation 
from a linear system and she
should give an assignment of the equation.
Bob is asked to assign a value to a random variable of that equation.
They win the game if Alice's assignment satisfies the equation and Bob's
assignment to the variable matches Alice's assignment.
A widely-used and thoroughly-studied example of a linear system game is
the Magic Square game \cite{magic_square}.
In this game, the linear system is
\begin{align*}
    &x_1 + x_2 + x_3 = 0 && x_4 + x_5 + x_6 = 0 &&
    x_7 + x_8 + x_9 = 0 \\
    &x_1 + x_4 + x_7 = 0 && x_2 + x_5 + x_8 = 1 &&
    x_3 + x_6 + x_9 = 0.
\end{align*}
Using two copies of the maximally entangled state
\begin{align*}
    \ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11}),
\end{align*}
the Magic square game can be won
with certainty.
It has been shown that if a strategy that can win this game almost perfectly, the shared state must be close to $\ket{EPR}^{\x 2}$ up to some local isometry \cite{wu2016}, 
so we can say that the Magic Square game can robustly self-test $\ket{EPR}^{\x 2}$.
The key observation that leads to the self-testing proof is that 
a winning strategy must contain observables $X$ and $Z$ that 
satisfy the anti-commutation relation 
\begin{align*}
    X Z = - Z X.
\end{align*}
Intuitively, we can think of the Magic Square game as a way to enforce the
anti-commutation relation.

Our linear system game is designed to enforce the relation 
\begin{align*}
    U O U\ct = O^r,
\end{align*}
for some integer $r$,
in the sense that the winning strategy contains binary observables
$M_1, M_2, M_3, M_4$ on Alice's side and 
$N_1, N_2, N_3, N_4$ on Bob's side such that 
\begin{align*}
    U = M_3M_4 = N_3N_4 && O = M_1M_2 = N_1N_2.
\end{align*}
This relation implies the eigenvalue of $O$ must be $\omega_d^j = e^{ij2\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root
is $r$. It also implies that $U$ is a permutation of the eigenbasis of $O$.
Winning this linear system game implies that Alice and Bob share a state
$\ket{\psi}$ such that
\begin{align*}
    O \x O \ket{\psi} = \ket{\psi}, && 
    U \x U \ket{\psi} = \ket{\psi}.
\end{align*}
These two relations are important for the self-testing argument
because
the relation $O \x O \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$
is spanned by tensor products of states in the eigenbasis of $O$;
and $U \x U \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$ is invariant
under the permutation induced by $U$. 
At this point, the eigenvalues of $O$ are unknown, so
further restricting the eigenvalues of $O$ requires another test, 
which will be introduced later.

The special feature of our linear system game is that the sizes
of the question sets for Alice and Bob are of order $\Theta(r)$,
and the answer sets are of size $\Theta(1)$.
Restricting $r \leq 5$ in our theorem implies that our linear system 
game only uses constant-sized question sets and constant-sized answer sets.
\carl{A reader may get lost at the last sentence -- you're jumping into the material too quickly without enough explanation.}
\hfc{Rewritten.}
% The number of variables and the number of equations of the linear system game depend linearly on $r$,
% which makes our correlation of size $\Theta(r^2)$.
% Unlike previous self-testing proofs, which try to enforce the anti-commutation relation
% $XZ = \omega_d^{-1} ZX$ between Pauli operators of dimension $d \geq 2$, 
% our approach is more succinct in terms of the size of the correlation but at a cost that
% it only works for odd prime $d$.
% The reason why we focus on this relation is that if we can certify that $O$ has one eigenvalue $\omega_d$
% for some $d$ with primitive $r$,
% then it guarantees that $O$ has eigenvalues $\omega_d^j$ for $j = 1 \dots d-1$ and $U$ only
% permutes the eigenvectors of $O$ in certain way.
% After knowing the eigenvalues of $O$, we can use infer the structure of the shared state $\ket{\psi}$
% based on the two relation of $\ket{\psi}$ imposed by the linear system game --
% $U_A \x U_B \ket{\psi} = \ket{\psi}$ and $O_A \x O_B \ket{\psi} = \ket{\psi}$.
% The two relations imply that $\ket{\psi}$ is spanned by eigenvectors of $O$ and its
% Schmidt coefficient follows some pattern that is invariant under the permutation by $U$.
% At this point, we can use the generalized swap isometry \cite{yang2013} to extract a copy of the 
% $(d-1)$-dimensional maximally entangled state. Note that our robust self-testing proof 
% follows a different line of arguments from what was originally
% proposed in Ref.~\cite{yang2013}.

The remaining question is how to certify a particular eigenvalue of $O$, so we
design a nonlocal test called the extended weighted CHSH test.
% Before going to the answer,
% we remark that 
% the other specialty of the linear system game is that it forces Alice and Bob to have binary observables
% whose products are the special unitaries $U$ and $O$, because the answers to the questions of the 
% linear system games are binary. 
% The idea of decompose the unitaries of arbitrary order into binary observables was also first introduced by Slofstra \cite{slofstra2017}.
% We use a different way to decompose the unitaries, which can be seen as the inverse of Jordan's lemma, 
% The fact that Alice and Bob only have binary observables make it easier for us 
% to compose the linear system game with another nonlocal test, which we call the extended weighted CHSH test.
The difference between a nonlocal game and a nonlocal test will be discussed later.
It is designed based on the $\alpha$-weighted CHSH inequality, which is defined by
\begin{align*}
    \I_\alpha = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2|\alpha|,
\end{align*}
where $M_x$ and $N_y$ for $x,y \in \{1, 2\}$ are some binary observables.
Define $\mu = \arctan(1/\alpha)$,
\begin{align*}
    \pauliz = \ketbra{0}{0} - \ketbra{1}{1} && \paulix = \ketbra{0}{1} + \ketbra{1}{0},
\end{align*}
which are the Pauli-Z and Pauli-X operators.
This inequality is maximally violated when the shared state is $\ket{EPR}$,
Alice's binary observables are
\begin{align*}
    M_1 = \pauliz && M_2 = \paulix,
\end{align*}
and Bob's binary observables are
\begin{align*}
    N_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix  && N_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix。
\end{align*}
We first prove that the maximal violation of $\I_\alpha$ can robustly self-test the shared
state $\ket{\psi}$ and the observables $M_1, M_2$ and $N_1, N_2$.
Then we noticed that 
\begin{align*}
    N_1N_2 = \cos(2\mu) \1  - \sin(2 \mu) \pauliz \paulix 
\end{align*}
has eigenvalues $e^{i 2\mu}$ and $e^{-i 2\mu}$.
Hence, in the extended weighted CHSH test, we set $\alpha = \cot( -\pi/d )$
for some odd prime $d$ whose primitive root is $r$,
and ask Alice and Bob
to reuse the observables $M_1, M_2$ and $N_1, N_2$，then we can certify that
the unitary $O = M_1M_2 = N_1N_2$ has eigenvalues $e^{i2\pi/d}$ and $e^{-i2\pi/d}$.
Combining this observation with the fact that $O$ satisfy the relation $UOU\ct = O^r$,
we can conclude that all the eigenvalues of $O$ are $\{ e^{ij 2\pi /d} \}_{j=1}^{d-1}$,
and the eigenspaces of all the eigenvalues have the same cardinality.
At this point, we has the explicit structure of $O$, so we 
can use the relations $U \x U \ket{\psi} = \ket{\psi}$ and $ O \x O \ket{\psi} = \ket{\psi}$
to prove the correlation $\fC(r, d)$ can robustly self-test 
a maximally entangled state of dimension $4(d-1)$.

\carl{This paragraph (also) will need more context.}
\hfc{Rewritten.}

Our contributions are four-fold.
\begin{enumerate}
    \item We identify the constant-sized question and answer sets that can be used to robustly self-test
    maximally entangled states with unbounded dimensions. Before our work, the most efficient way
    was to use $O(\log d)$-sized question and answer sets to robustly self-test
    the maximally entangled state of dimension $d = 2^n$ \cite{lowdegree}.
    \item Our self-testing proof demonstrate a new way to apply the generalized swap-isometry
    proposed in Ref.~\cite{yang2013} to robustly self-test a maximally entangled state of large lcoal
    dimension. This is the first application of the generalized swap-isometry in the robust self-testing proof.
    We believe it can be applied to prove the family of correlations proposed in Ref.~\cite{coladan2017all}
    are also robust.
    \item We demonstrate how to enforce relations between operators of large but fixed dimension in a 
    binary linear system game. Before our work, only the anti-commutation relation between $2$-dimensional
    Pauli operators can be enforced in a binary linear system game.
    \item Our result gives us deeper understanding of the set of quantum correlations.
    In previous works that proved the non-closeness of the set of quantum correlations
    \cite{slofstra2017}, 
    lower bounds of the entanglement required to achieve certain correlations are identified.
    Our work discovers a large family of correlations where we know exactly the amount of entanglement
    required to achieve each of the correlations in this family. 
\end{enumerate}

\textbf{Structure of the paper}.
We start with notations and background information in \cref{sec:prelim}.
Since the correlation we designed can win a special linear system game and satisfy
an extended weighted CHSH test, we introduce the linear system game
in \cref{sec:lsg} and the self-testing properties of the extended weighted CHSH inequality in \cref{sec:chsh}. 
Then we give the correlation $\fC(d,r)$ and the ideal strategy to generate it in \cref{sec:full_test}.
In the end, we give the robust self-testing proof in \cref{sec:main}.

>>>>

% AMS
\usepackage{amsmath,amssymb,amsfonts,amsthm,amstext}
\usepackage{bbm}

@@

\renewcommand{\Re}{\operatorname{Re}}
\renewcommand{\Im}{\operatorname{Im}}
\DeclareMathOperator{\vc}{vec}
\DeclareMathOperator{\spn}{span}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\spec}{spec}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\hook}{hook}
\DeclareMathOperator*{\E}{\mathbb{E}}
\DeclareMathOperator{\supp}{supp}

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\EXT}{EXT}
\newcommand{\LS}{LS}
\newcommand{\COMM}{COMM}
\newcommand{\EPR}[1]{\Sigma^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\tO}{\tilde{O}}
\newcommand{\tP}{\tilde{P}}
\newcommand{\tQ}{\tilde{Q}}
\newcommand{\tM}{\tilde{M}}
\newcommand{\tN}{\tilde{N}}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}
\newcommand{\nr}{n(r)}
\newcommand{\mr}{m(r)}
\newcommand{\ux}{\underline{x}}
\newcommand{\uc}{\underline{c}}
\newcommand{\ua}{\underline{a}}
\newcommand{\ub}{\underline{b}}
\newcommand{\fC}{\mathfrak{C}}
\newcommand{\ba}{\pmb{a}}
\newcommand{\bb}{\pmb{b}}
\newcommand{\bc}{\pmb{c}}
\newcommand{\bS}{\mathbbmtt{S}}

@@

\author[1]{Honghao Fu}

@@

\affil[1]{Department of Computer Science, Institute for Advanced Computer Studies, and Joint Center for Quantum \break Information and Computer Science, University of Maryland, College Park, MD 20742, USA}
%\affil[2]{National Institute of Standards and Technology, 100 Bureau Dr., Gaithersbug, MD 20899, USA}
\maketitle

\begin{abstract}
	We show that for any prime odd integer $d$, there exists a correlation of size $\Theta(r)$ 
	that can robustly self-test a maximally entangled state of dimension $4d-4$,
	where $r$ is the smallest multiplicative generator of $\Zd$.
	The construction of the correlation uses the embedding procedure
	proposed by Slofstra (\textit{Forum of Mathematics, Pi.} Vol.~$7$ Cambridge University Press, $2019$).
	Since there are 
	infinitely many prime numbers whose smallest multiplicative generator
	is at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimensions.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
The certification of a quantum device is an important building block
for many quantum information processing tasks, especially
when the devices are provided by some untrusted vendor.
We would like such certification to be done based solely on
the observed measurement statistics and with the only assumption that
any local device cannot communicate their own
inputs to the other local devices. 
The measurement statistics are referred to as correlations.

It has been shown that certain quantum correlations require the distant parties to share
a particular entangled state up to some local isometry. 
This phenomenon is referred to as self-testing.  
If we can further prove that, when the observed correlation deviates 
from the ideal one to some extent, 
the shared state is close to the ideal state up to some local isometry,
then we say the self-test is robust.

Self-testing is powerful because only classical interactions are performed.
Hence, it allows a classical party to delegate quantum computations to some untrusted service provider
and verify that the computations are performed
honestly and correctly \cite{ruv2013,coladan2017verifier}.
It also becomes a critical component of the security proofs of device-independent quantum cryptographic protocols
\cite{mayersyao,vv2014,miller2017,fu2018,eat2018}.
Since the setting of interactive proof systems is similar to a self-test, self-testing arguments also help to prove
lower bounds of the computational power of entanglement-assisted
multiprover interactive proof systems \cite{fitzsimons2019, neexp}.

The case of robust self-testing of the EPR pair, 
\begin{align*}
    \ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11}),
\end{align*}
is fully understood.
The techniques for this case are 
first introduced in \cite{mckague2012}, then improved in \cite{bamps2015}. 
Robust self-testing of partially entangled qubits is proved later in
\cite{yang2013}, which also proposed an generalized swap-isometry
that can be used to robustly self-test large dimensional maximally entangled states.
Robust self-testings of tensor product of maximally and partially entangled qubits 
are proved in \cite{coladan2016parallel,natarajan2017,lowdegree},
with the last one being the one with the smallest input and output alphabets.
Self-testing of all pure bipartite entangled states is proved in \cite{coladan2017all}.
The authors in \cite{coladan2017all} constructed a family of correlations such
that an entangled state of any local dimension has
a self-testing correlation in this family.
% One can also self-test many copies of the $2$-dimensional EPR
% pair in parallel \cite{mckague2016,natarajan2017,coladan2016parallel}.
% The most efficient way uses $O(\log n)$ bits question and
% answers to self-test $n$ copies of $2$-dimensional EPR
% pair \cite{lowdegree}.
% Self-testing general $d$-dimensional EPR pairs is a harder task.
% Coladangelo, Goh and Scarani has shown that all pure bipartite entangled states can be self-tested \cite{coladan2017all}
To generate a correlation in the family, Alice and Bob
use constant-sized input alphabets but $\Theta(d)$-sized output alphabets, 
where $d$ is the local dimension of the entangled state. 
This is the only result about self-testing the general $d$-dimensional entangled state so far.
However, proving the robustness of this family of correlations remains an open problem.

Our work aims at answering two open questions.
The first one is whether maximally entangled states with large local dimension
can be self-tested with constant-sized input and output alphabets, 
which are independent of the local dimension of the self-tested state.
For comparisons, all the correlations used in the results listed above
have either input or output alphabets with sizes dependent on the
local dimension of the entangled state.
The second one is how to robustly self-test maximally entangled states
with large local dimension and no tensor product structure. 
We give an affirmative answers to the first question and
make significant progress in answering the second question
by proving the following theorem.
\begin{theorem}[Informal]
\label{thm:inf}
	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
	the maximally entangled state of local dimension $4(d-1)$ can be robustly self-tested 
	with constant-sized question and answer alphabets.
\end{theorem}
The formal statement of this theorem is given in \cref{thm:self-test} and \cref{thm:infty}.

The set $D$ is, specifically, the set of all 
odd prime numbers whose smallest primitive root 
is either $2$, $3$, or $5$, 
We say that $r$ is a primitive root of $d$ if $r$ is the 
multiplicative generator of the group $\Zd$.
It has been shown that $D$ has infinitely many elements \cite{murty1988}.

To prove \cref{thm:inf}, we construct a correlation with $\Theta(r)$-sized
input and constant-sized output alphabets
for each odd prime number $d$ whose smallest primitive root is $r$.
This correlation is denoted by $\fC(d,r)$.
Note that although the size of the input or output alphabet of $\fC(d,r)$ does not depend on $d$, 
the distributions in $\fC(d,r)$ do. 
Once we prove $\fC(d,r)$ can robustly self-test a maximally entangled
state of dimension $4(d-1)$, we apply it to all $d \in D$
and prove \cref{thm:inf}.
%Then the self-testing property of this correlation is 
%given in the following theorem.
%\begin{theorem}[Informal]
%\label{thm:pr_2}
%	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
%	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
%\end{theorem}

The correlation $\fC(d,r)$ contains a winning correlation of a specially-designed binary linear system game.
In a general linear system game, Alice is given a random equation 
from a linear system and she
should give an assignment to each variable of the equation.
Bob is asked to assign a value to a random variable of that equation.
They win the game if Alice's assignment satisfies the equation and Bob's
assignment to the variable matches Alice's assignment.
A widely-used and thoroughly-studied example of a linear system game is
the Magic Square game \cite{magic_square}.
In this game, the linear system is
\begin{align*}
    &x_1 + x_2 + x_3 = 0 && x_4 + x_5 + x_6 = 0 &&
    x_7 + x_8 + x_9 = 0 \\
    &x_1 + x_4 + x_7 = 0 && x_2 + x_5 + x_8 = 1 &&
    x_3 + x_6 + x_9 = 0.
\end{align*}
Using two copies of $\ket{EPR}$
the Magic square game can be won with certainty.
It has been shown that if a strategy that can win this game almost perfectly, 
the shared state must be close to $\ket{EPR}^{\x 2}$ up to some local isometry \cite{wu2016}, 
so we can say that the Magic Square game can robustly self-test $\ket{EPR}^{\x 2}$.
The key observation that leads to the self-testing proof is that 
a winning strategy must contain binary observables $X$ and $Z$ that 
satisfy the anti-commutation relation 
\begin{align*}
    X Z = - Z X.
\end{align*}
Intuitively, we can think of the Magic Square game as a way to enforce the
anti-commutation relation \cite{coladan2017}.

Our linear system game is designed to enforce the relation 
\begin{align*}
    U O U\ct = O^r,
\end{align*}
for unitaries $U$ and $O$, and some integer $r$.
It implies that the winning strategy contains binary observables
$M_1, M_2, M_3, M_4$ on Alice's side and 
$N_1, N_2, N_3, N_4$ on Bob's side such that 
\begin{align*}
    U = M_3M_4 = N_3N_4 && O = M_1M_2 = N_1N_2.
\end{align*}
This relation implies the eigenvalues of $O$ must be $\omega_d^j = e^{ij2\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root is $r$. 
It also implies that $U$ is a permutation of the eigenbasis of $O$.
Winning this linear system game implies that Alice and Bob share a state
$\ket{\psi}$ such that
\begin{align*}
    O \x O \ket{\psi} = \ket{\psi}, && 
    U \x U \ket{\psi} = \ket{\psi}.
\end{align*}
These two relations are important for the self-testing argument.
The relation $O \x O \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$
is spanned by tensor products of states in the eigenbasis of $O$.
The relation $U \x U \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$ is invariant
under the permutation induced by $U$. 
At this point, the eigenvalues of $O$ are unknown, so
certifying the eigenvalues of $O$ requires another test, 
which will be introduced later.

The special feature of our linear system game is that the sizes
of the question sets for Alice and Bob are of order $\Theta(r)$,
and the answer sets are of size $\Theta(1)$.
Restricting $r \leq 5$ as in \cref{thm:inf} implies that our linear system 
game only uses constant-sized question sets and constant-sized answer sets.

% The number of variables and the number of equations of the linear system game depend linearly on $r$,
% which makes our correlation of size $\Theta(r^2)$.
% Unlike previous self-testing proofs, which try to enforce the anti-commutation relation
% $XZ = \omega_d^{-1} ZX$ between Pauli operators of dimension $d \geq 2$, 
% our approach is more succinct in terms of the size of the correlation but at a cost that
% it only works for odd prime $d$.
% The reason why we focus on this relation is that if we can certify that $O$ has one eigenvalue $\omega_d$
% for some $d$ with primitive $r$,
% then it guarantees that $O$ has eigenvalues $\omega_d^j$ for $j = 1 \dots d-1$ and $U$ only
% permutes the eigenvectors of $O$ in certain way.
% After knowing the eigenvalues of $O$, we can use infer the structure of the shared state $\ket{\psi}$
% based on the two relation of $\ket{\psi}$ imposed by the linear system game --
% $U_A \x U_B \ket{\psi} = \ket{\psi}$ and $O_A \x O_B \ket{\psi} = \ket{\psi}$.
% The two relations imply that $\ket{\psi}$ is spanned by eigenvectors of $O$ and its
% Schmidt coefficient follows some pattern that is invariant under the permutation by $U$.
% At this point, we can use the generalized swap isometry \cite{yang2013} to extract a copy of the 
% $(d-1)$-dimensional maximally entangled state. Note that our robust self-testing proof 
% follows a different line of arguments from what was originally
% proposed in Ref.~\cite{yang2013}.

The remaining question is how to certify eigenvalues of $O$, so we
design a nonlocal test called the extended weighted CHSH test.
% Before going to the answer,
% we remark that 
% the other specialty of the linear system game is that it forces Alice and Bob to have binary observables
% whose products are the special unitaries $U$ and $O$, because the answers to the questions of the 
% linear system games are binary. 
% The idea of decompose the unitaries of arbitrary order into binary observables was also first introduced by Slofstra \cite{slofstra2017}.
% We use a different way to decompose the unitaries, which can be seen as the inverse of Jordan's lemma, 
% The fact that Alice and Bob only have binary observables make it easier for us 
% to compose the linear system game with another nonlocal test, which we call the extended weighted CHSH test.
The difference between a nonlocal game and a nonlocal test will be discussed later.
The combination of a linear system game with 
a nonlocal test in the construction of $\fC(d,r)$ 
is a new way to use a linear system game for robust self-testing.
It distinguishes our approach from all the previous ones.

The extended weighted CHSH test is designed based on the $\alpha$-weighted CHSH inequality, 
\begin{align*}
    \I_\alpha = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2|\alpha|,
\end{align*}
where $M_x$ and $N_y$ for $x,y \in \{1, 2\}$ are some binary observables.
Define $\mu = \arctan(1/\alpha)$,
\begin{align*}
    \pauliz = \ketbra{0}{0} - \ketbra{1}{1} && \paulix = \ketbra{0}{1} + \ketbra{1}{0},
\end{align*}
which are the Pauli-Z and Pauli-X operators.
This inequality is maximally violated when the shared state is $\ket{EPR}$,
Alice's binary observables are
\begin{align*}
    \tM_1 = \pauliz && \tM_2 = \paulix,
\end{align*}
and Bob's binary observables are
\begin{align*}
    \tN_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix  && \tN_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix。
\end{align*}
We first prove that the maximal violation of $\I_\alpha$ can robustly self-test the shared
state $\ket{\psi}$ and the observables $\tM_1, \tM_2$ and $\tN_1, \tN_2$ in \cref{sec:ext_chsh}.
Then we notice that 
\begin{align*}
    \tN_1\tN_2 = \cos(2\mu) \1  - \sin(2 \mu) \pauliz \paulix 
\end{align*}
has eigenvalues $e^{i 2\mu}$ and $e^{-i 2\mu}$.

Therefore, in the extended weighted CHSH test, we set $\alpha = \cot( -\pi/d )$
for some odd prime $d$ whose primitive root is $r$,
and ask Alice and Bob
to reuse the observables $M_1, M_2$ and $N_1, N_2$ defined in $\LS(r)$. Then we can certify that
the unitary $O = M_1M_2 = N_1N_2$ has eigenvalues $e^{i2\pi/d}$ and $e^{-i2\pi/d}$.
Combining this observation with the fact that $O$ satisfy the relation $UOU\ct = O^r$,
we can conclude that all the eigenvalues of $O$ are $\{ e^{ij 2\pi /d} \}_{j=1}^{d-1}$,
and the eigenspaces of all the eigenvalues have the same cardinality.

At this point, we have the explicit structure of $O$, so we 
can use the relations $U \x U \ket{\psi} = \ket{\psi}$ and $ O \x O \ket{\psi} = \ket{\psi}$
to prove the correlation $\fC(r, d)$ can robustly self-test 
a maximally entangled state of dimension $4(d-1)$,
\begin{align*}
    \left(\frac{1}{\sqrt{d}} \sum_{j=1}^{d-1}\ket{j}\ket{d-j}\right)\x 
    \ket{EPR}^{\x 2}.
\end{align*}

In the proof, we demonstrate a new way to apply the generalized swap-isometry
proposed in \cite{yang2013} to robustly self-test a maximally entangled state of large local
dimension. This is the first application of the generalized swap-isometry in the robust self-testing proof.

Our contributions are:
\begin{enumerate}
\item We identify a family of correlations with constant-sized input and output alphabets that can be used to robustly self-test
maximally entangled states with unbounded local dimensions. Before our work, the most efficient way 
was to use $O(\log d)$-sized input and $O(\log \log d)$-sized output alphabets to robustly self-test
the maximally entangled state of dimension $d = 2^n$ \cite{lowdegree}.

\item Our result gives us deeper understandings of the set of quantum correlations.
In previous works that proved the non-closeness of the set of quantum correlations \cite{slofstra2017, slofstra2018}, 
lower bounds of the entanglement required to achieve certain correlations are identified.
We discover a large family of correlations such that we know exactly the entangled state
required to achieve each of the correlations in this family. 
\end{enumerate}

\textbf{Structure of the paper}.
We start with notations and background information in \cref{sec:prelim}.
Since the correlation we designed can win a special linear system game and satisfy
an extended weighted CHSH test, we introduce the linear system game
in \cref{sec:lsg} and the extended weighted CHSH test in \cref{sec:ext_chsh}. 
Then we give the correlation $\fC(d,r)$ and the ideal strategy to generate it in \cref{sec:full_test}.
In the end, we give the robust self-testing proof in \cref{sec:main}.
